Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-08-13 paper/post_tci.tex
Added all new post-TCI images; updated sprouts results in paper

 \begin{figure}[t]
\centering
	\includegraphics[width=0.45\textwidth]{../images/story/story.png}
        \caption{Illustration of the use of various priors in 
          reconstruction as the number of views reduces. In all cases,
          the ground truth (260$\times$260) appears in the top left.
          For extremely large number of views (800 views), the FBP
          reconstruction (first column) is of very good quality
          (Structural Similarity Index Metric, SSIM=0.92). As the
          number of views become limited (100 views), the
          reconstruction using a general data-independent prior such as Total Variation (TV, middle column) is
          better both visually and quantitatively than FBP (SSIM of
          0.96 vs 0.82). If the number of views is drastically reduced
          (20 views), the presence of both TV prior and object
          prior together improves the reconstruction (SSIM=0.91) when compared
          to presence of only TV prior (SSIM=0.87) or no prior
          (SSIM=0.64).}
 \label{fig:story}
 \end{figure}

@@

\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/very_few_views/colorTestIm.png}}}\hfill
\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/fbp.png}}\hfill
\subcaptionbox{TV}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/tv_lambdaTV_0.036.png}}\hfill
\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
\subcaptionbox{Weights map}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/weightsIm_kk_30_lambda_prior_1.100000.png}}

@@

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/input_roi.png}}}
\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/FBP_cropped.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/TV_cropped.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/weighted_prior_cropped.png}}
\caption{Reconstruction of 2D okra from 48 projection views
   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts. The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
\label{fig:okra_3D_results}
\end{figure}

@@

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.29\columnwidth]{../images/sprouts/post_TCI/20_views/testIm.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/20_views/fbp.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/20_views/tv_lambdaTV_0.100.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
\caption{Reconstruction of 2D sprouts from 20 projection views
   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts. The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
\label{fig:sprouts3D_results}
\end{figure}

@@

\subsubsection{\textbf{Sprouts}}
\label{Sec:sprouts_spatially_varying}
 %-----------------------------sprouts 3D results
\begin{figure}[!h]
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/testIm.png}}
%\captionsetup{labelformat=empty}
        \caption{Test}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/fbp.png}
%\captionsetup{labelformat=empty}
        \caption{FDK, no prior}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/tv_lambdaTV_0.100.png}
%\captionsetup{labelformat=empty}
        \caption{TV, no prior}
     \end{subfigure}\\
%\quad
%    \begin{subfigure}[b]{0.3\linewidth}
%        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
%\captionsetup{labelformat=empty}
%        \caption{Uniform\\ Prior}
%     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}
%\captionsetup{labelformat=empty}
        \caption{Spatially-Varying\\ prior}
    \end{subfigure}
    %\quad
     \caption{Reconstruction of 2D sprouts from 20 projection views
   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts. The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.} 
\label{fig:sprouts_3D_results}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}

%--------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{SSIM of reconstructed sprouts from various
    methods. For 3D, the RoI spans 7 consecutive slices where the test is
    different from all of the previously scanned objects. The SSIM of ground-truth (ideal reconstruction) is 1.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
    TV\end{tabular}} \\ \hline \textbf{2D} & 0
& 0 & \textcolor{red}{0} \\ \hline \textbf{3D} & 0.67 & 0.73 & \textcolor{red}{0.82}
\\ \hline
\end{tabular}
\label{table:sprouts_ssim}
\end{table}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_5_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_10_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_20_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_30_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_40_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_50_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_60_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_70_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_80_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_90_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_100_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_130_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_5_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_10_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_20_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_30_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_40_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_50_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_60_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_70_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_80_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_90_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_100_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_130_lambda_prior_0.700000.png}

>>>>

 \begin{figure}[t]
\centering
	\includegraphics[width=0.45\textwidth]{../images/story/post_TCI/story.png}
        \caption{Illustration of the use of various priors in 
          reconstruction as the number of views reduces. In all cases,
          the ground truth (260$\times$260) appears in the top left.
          For extremely large number of views (800 views), the FBP
          reconstruction (first column) is of very good quality
          (Structural Similarity Index Metric, SSIM=0.92). As the
          number of views become limited (100 views), the
          reconstruction using a general data-independent prior such as Total Variation (TV, middle column) is
          better both visually and quantitatively than FBP (SSIM of
          0.96 vs 0.82). If the number of views is drastically reduced
          (20 views), the presence of both TV prior and object
          prior together improves the reconstruction (SSIM=0.91) when compared
          to presence of only TV prior (SSIM=0.87) or no prior
          (SSIM=0.64).}
 \label{fig:story}
 \end{figure}

@@

\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/colorTestIm.png}}}\hfill
\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp.png}}\hfill
\subcaptionbox{TV}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_lambdaTV_0.036.png}}\hfill
\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
\subcaptionbox{Weights map}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weightsIm_kk_30_lambda_prior_1.100000.png}}

@@

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/input_roi.png}}}
\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/FBP_cropped.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/TV_cropped.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_prior_cropped.png}}
\caption{Reconstruction of 2D okra from 48 projection views
   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts. The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
\label{fig:okra_3D_results}
\end{figure}

@@

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.29\columnwidth]{../images/sprouts/post_TCI/2D/20_views/testIm_roi.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_lambdaTV_0.100.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
\caption{Reconstruction of 2D sprouts from 20 projection views
   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts. The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
\label{fig:sprouts3D_results}
\end{figure}

@@

\subsubsection{\textbf{Sprouts}}
\label{Sec:sprouts_spatially_varying}
 %-----------------------------sprouts 3D results

%--------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{SSIM of reconstructed sprouts from various
    methods. For 3D, the RoI spans 7 consecutive slices where the test is
    different from all of the previously scanned objects. The SSIM of ground-truth (ideal reconstruction) is 1.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
    TV\end{tabular}} \\ \hline \textbf{2D} & 0.67
& 0.82 & \textcolor{red}{0.86} \\ \hline \textbf{3D} & 0.67 & 0.73 & \textcolor{red}{0.82}
\\ \hline
\end{tabular}
\label{table:sprouts_ssim}
\end{table}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_5_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_10_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_20_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_30_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_40_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_50_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_60_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_70_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_80_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_90_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_100_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_130_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_5_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_10_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_20_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_30_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_40_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_50_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_60_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_70_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_80_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_90_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_100_lambda_prior_0.700000.png}

@@

        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_130_lambda_prior_0.700000.png}
